\chapter{Reported Vulnerabilities} \label{ch:reported-vulns}
This chapter explains which vulnerabilities were reported to the manufacturer as well as a detailed timeline of events that took place during the responsible disclosure process and the two CVEs connected to this thesis.

Two vulnerabilities identified in chapter \ref{ch:pentesting} were deemed sever enough to report to the manufacturer:
\begin{enumerate}
    \item The RF replay-attack vulnerability identified in section \ref{ch:pentesting:replay}, which allows an attacker to for example disarm an armed system.
    \item The repudiation vulnerability arising from the absence of notifications to the owner of the system during an ongoing RF jamming-attack (see section \ref{ch:pentesting:rf-jamming}).
\end{enumerate}

\section{Timeline of events}
The following outlines the timeline of events during the responsible disclosure process.

\begin{itemize}
    \item \verb![2021-06-15]! Securitas is contacted through their customer support and responsible disclosure form, and are notified that vulnerabilities might exist in the system.
    \item \verb![2021-07-07]! Terms are agreed upon by both parties and the two vulnerabilities are officially disclosed and described in detail to the manufacturer.
    \newpage
    \item \verb![2021-08-23]! Securitas acknowledges that both vulnerabilities are present in the system. Additionally, Securitas confirms that their hardware vendor has started developing a security patch. A bug bounty is offered and the two vulnerabilities are deemed by the manufacturer to have a CVSS score of \texttt{5.5} and \texttt{4.5} respectively.
    \item \verb![2021-08-27]! The two vulnerabilities are reported to MITRE and two CVEs are requested.
    \item \verb![2021-08-29]! MITRE responds and accepts both CVE requests. Two CVE ids are reserved:
        \begin{itemize}
            \item \textbf{CVE-2021-40170} for the RF replay-attack vulnerability.
            \item \textbf{CVE-2021-40171} for the RF jamming-attack vulnerability.
        \end{itemize}
    \item \verb![2021-09-21]! A security patch is rolled out to all systems and Securitas' customers are officially notified via email of the vulnerabilities as well as the security patch.
    \item \verb![2021-09-25]! The responsible disclosure window ends and the thesis as well as the two CVEs are officially published.
\end{itemize}